hbm_paper_results

### 2024-02-08 paper_main_results.Rmd
checking over, editing figs

global_cent_errs_plot <- global_abs.diffs %>%
  dplyr::filter(dataset == "cf.lm" | dataset == "cf.gam" | dataset == "cf.gamlss") %>% #drop refA levels
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         pheno = factor(pheno, levels = c("WMV", "GMV", "sGMV", "Ventricles"), ordered = TRUE),
         abs.diff = abs.diff*100) %>% #for visuals
  ggplot(aes(pheno, abs.diff)) +
  geom_violin(aes(x=pheno, y=abs.diff, fill=dataset, color=dataset), scale="count") +
  theme_linedraw(base_size = 11) +
  scale_fill_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  #WMV
geom_signif(y_position = c(29, 30.5, 4), xmin = c(0.7, 0.7, 1), 
              xmax = c(1, 1.3, 1.3), annotation = c("***","***", "***"),
              tip_length = 0, vjust = 0.6) +
  #GMV
  geom_signif(y_position = c(30, 31.5, 3), xmin = c(1.7, 1.7, 2), 
              xmax = c(2, 2.3, 2.3), annotation = c("***","***", "***"),
              tip_length = 0, vjust = 0.6) +
  #sGMV
  geom_signif(y_position = c(28, 29.5, 2.8), xmin = c(2.7, 2.7, 3), 
              xmax = c(3, 3.3, 3.3), annotation = c("***","***", "***"),
              tip_length = 0, vjust = 0.6) +
  #Ventricles
  geom_signif(y_position = c(24, 25.5, 7.5), xmin = c(3.7, 3.7, 4), 
              xmax = c(4, 4.3, 4.3), annotation = c("***","***", "***"),
              tip_length = 0, vjust = 0.6) +
  labs(y="Magnitude Centile Error", x = "Phenotype") +
  theme(plot.title = element_text(size=12)) +
  ggtitle("Magnitude error in centile scores")
global_cent_errs_plot
# ggsave("figs/global_centile_errors.jpeg", global_cent_errs_plot)
```

@@

p_diff_annotate <- annotate_figure(p_diff, top = text_grob("Magnitude Centile Errors", color = "black", hjust = 0, x = 0.06))
p_diff_annotate
```

@@

```{r}
subj_sum.df %>%
  dplyr::filter(dataset == "cf.gamlss" | dataset == "cf.gam" | dataset == "cf.lm") %>%
  mutate(mean_cent_abs.diff = mean_cent_abs.diff*100) %>% #for visuals
  ggplot() +
  geom_boxplot(aes(x=sex, y=mean_cent_abs.diff, fill=sex)) +
  labs(y= "Magnitude Centile Error", x = "ComBat Configurations") +
  facet_wrap(~dataset) +
  theme(legend.position="none") +
  ggtitle("Within-subject mean magnitude of error in centile scores across ComBat configurations")

@@

@@

big_violin_plt <- plt.df %>%
  ggplot(aes(x=pheno, y=diff)) +
  geom_violin(aes(x=interaction(pheno,pheno_cat, sep = "&"), y=diff, fill=sex, color=sex)) +
  # geom_violin(aes(fill=sex, color=sex)) +
  theme_linedraw(base_size = 11) +
  labs(y="Centile Error", x = "Brain Feature") +
  theme(plot.title = element_text(size=12), axis.ticks.x = element_blank(), axis.text.x = element_blank(), panel.spacing.x = unit(.1, "lines"), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  stat_pvalue_manual(stat.test2, label = "p.adj.signif", label.size = 3, tip.length = 0, hide.ns = TRUE, remove.bracket = TRUE) +
  # facet_grid2(dataset ~ pheno_cat, labeller=labeller(dataset=dataset_names), scales="free_x", space = "free_x", switch="x", strip = custom_strip) +
  facet_wrap(~dataset, labeller=labeller(dataset=dataset_names), nrow=2) +
  guides(x = ggh4x::guide_axis_nested(delim = "&")) +
  theme(plot.title = element_text(size=12), axis.ticks.x = element_blank(), axis.text.x = element_blank(), ggh4x.axis.nesttext.x = element_text(angle = 90, vjust=0.4), legend.position="top") +
  labs(fill = "Sex", color="Sex") +
  ggtitle("Male and female centile errors")
big_violin_plt
ggsave("figs/big_sex_violin_plt.jpeg", big_violin_plt, width=12, height=6, units="in")
```

@@

sex.var.plot <- ggplot(sex.var.plot.df) +
  theme_linedraw(base_size=12) +
  ggseg::geom_brain(atlas = dk_nomed, 
             position = position_brain(hemi ~ side),
             aes(fill = median_sex_diff)) +
  #scale_fill_gradient2() +
  # ggseg::geom_brain(data=med_wall, atlas = dk, 
  #            position = position_brain(hemi ~ side),
  #            aes(fill=median_sex_diff)) +
  facet_grid(dataset ~ pheno_cat, labeller = labeller(dataset = as_labeller(dataset_names))) + 
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA), aspect.ratio=2/3, plot.margin = margin(1,1,1,1, 'pt')) +
  paletteer::scale_fill_paletteer_c("grDevices::Cork", name = "Sex Effect", limits = c(-6, 6)) #
sex.var.plot
```

@@

sex.var.plot.global <- ggplot(sex.var.plot.global.df) +
  geom_rect(data = tp, fill="gray", xmin = -Inf,xmax = Inf,
            ymin = -Inf, ymax = Inf, alpha = 0.4) +
  ggseg::geom_brain(atlas = aseg_cerebrum, 
             aes(fill = median_sex_diff),
             side = c("coronal")) +
  #scale_fill_gradient2() +
  facet_grid(dataset~pheno_cat) + 
  theme_linedraw(base_size=12) +
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA), aspect.ratio=, plot.margin = margin(1,1,1,1, 'pt'), strip.text.y = element_blank()) +
  paletteer::scale_fill_paletteer_c("grDevices::Cork",  limits = c(-6, 6), name = "Sex Effect") #,
# sex.var.plot.global
```

@@

centile error diffs
```{r}
centile.t.tests(no_ext, feature_list=pheno_abs.diff.list)
```

@@

@@

```{r}
subj_sum.df %>%
  dplyr::filter(dataset == "cf.gamlss" | dataset == "cf.gam" | dataset == "cf.lm") %>%
  ggplot() +
  geom_boxplot(aes(x=sex, y=mean_z_abs.diff, fill=sex)) +
  labs(y= "Magnitude Z Error", x = "ComBat Configurations") +
  facet_wrap(~dataset, scales="free_y") +
  theme(legend.position="none") +
  ggtitle("Within-subject mean magnitude of error in z-scores across ComBat configurations")

@@

```{r, warning=FALSE}
z.sex_t_tests_in_feat.df <- sex.bias.feat.t.tests(diffs.df, feature_list=z.pheno_diff_list)

@@

### W/o extremes
Are extreme z-scores (<-2 and >2) driving observed results?

@@

z.no.ext_merge %>%
  ggplot() +
  geom_boxplot(aes(x=type, y=z_abs.diff, fill=dataset)) +
  ggtitle("W/in feature average magnitude of centile error, w/ and w/o extreme subjects")
```

@@

wmv_centile_fan <- ggplot(wmv.df) +
  geom_jitter(data = ukb_cn_df, aes(x=ukb_cn_df$age_years, y=ukb_cn_df$WMV), alpha=0.4, width=.2, color="lightgray") +
  #scale_colour_manual(values=c("#5AAE61FF", "#9970ABFF")) +
  geom_line(aes(x=age_years, y=centile_1, color=dataset, linetype=dataset)) +
  geom_line(aes(x=age_years, y=centile_2, color=dataset, linetype=dataset)) +
  #geom_line(aes(x=age_years, y=centile_3, color=dataset, linetype=dataset)) +
  # geom_line(aes(x=age_years, y=centile_4, color=dataset, linetype=dataset)) +
  geom_line(aes(x=age_years, y=centile_5, color=dataset, linetype=dataset), linewidth=1.5) +
  # geom_line(aes(x=age_years, y=centile_6, color=dataset, linetype=dataset)) +
  # geom_line(aes(x=age_years, y=centile_7, color=dataset, linetype=dataset)) +
  geom_line(aes(x=age_years, y=centile_8, color=dataset, linetype=dataset)) +
  geom_line(aes(x=age_years, y=centile_9, color=dataset, linetype=dataset)) +
  facet_wrap(~sex) + 
  scale_linetype_manual(values = c('ukb-CN-simsites'= "dotted", cf.gam = "solid", cf.gamlss = "solid", cf.lm = "solid"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values = c('ukb-CN-simsites'= "black", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) + 
  geom_label(data=tmp_labels, aes(x=age_years, y=value, label=as.character(centile)), nudge_x = 0.35, size=2) +
  xlab("Age (yrs)") + ylab("Volume (mm3)") +
  theme_linedraw(base_size = 11) +
  theme(plot.title = element_text(size=12), legend.position="bottom") +
  labs(title="White matter volume brain charts")
wmv_centile_fan
```
Look at other phenotypes

@@

## METHODS FIG

toy brain chart for figs

@@

## FIGURE 1

not sure whether to include
```{r}
#look at sex distributions of ppts across sites
data.p <- subj_sum.df %>%
  count(sim.site, sex) %>% 
  group_by(sim.site) %>%
  mutate(prop = n / sum(n)) %>%
  ggplot(aes(x = sim.site, y = prop, fill = sex)) +
  geom_col() +
  theme_linedraw(base_size = 11) +
  ggtitle("Distributions of male and female subjects across simulated sites")
```

@@

```{r}
fig_1 <- ggarrange(
  wmv_centile_fan,
  ggarrange(global_cent_errs_plot, p_diff_annotate, ncol=1, nrow=2, heights = c(1.2, 2), common.legend = FALSE, labels=c("B", "C")),
  ncol=2, nrow=1, 
  labels=c("A", NA),
  widths=c(1.1, 1)
  #hjust=0.01,
  # align = "hv"
  )

fig_1_annotate <- annotate_figure(fig_1, top = text_grob("Figure 1. Choice of ComBat configuration can induce errors in brain feature centile scores",
               color = "black", hjust = 0, x = 0))
fig_1_annotate
ggsave("figs/figure_1.jpeg", fig_1_annotate, width=11, height=7, units="in")
```

@@

fig_2 <- ggarrange(
  ggarrange(blank, 
            annotate_figure(
              ggarrange(sex.var.plot.global, sex.var.plot,
  ncol=2, nrow=1, 
  widths = c(1, 3.25),
  hjust=0.01,
  align = "hv",
  common.legend = TRUE, legend = "right"
  ), top = text_grob("Differences in males' and females' median centile errors", color = "black", hjust = 0, x = 0)),
  blank,
  ncol=3, nrow=1,
  widths=c(.5, 1, .5)),
  big_violin_plt,
  ncol=1, nrow=2, 
  #labels=c("A", "B"),
  #hjust=0.01,
  # align = "hv",
  heights=c(1, 1.8),
  common.legend = FALSE,
  labels=c("A", "B")
  )
# fig_2

fig_2_annotate <- annotate_figure(fig_2, top = text_grob("Figure 2. Sex-biases in centile score errors across ComBat configurations", color = "black", hjust = 0, x = 0))
fig_2_annotate
ggsave("figs/figure_2.jpeg", fig_2_annotate, width=11.5, height=10, units="in")
```

>>>>

global_cent_errs_plot <- global_abs.diffs %>%
  dplyr::filter(dataset == "cf.lm" | dataset == "cf.gam" | dataset == "cf.gamlss") %>% #drop refA levels
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         pheno = factor(pheno, levels = c("WMV", "GMV", "sGMV", "Ventricles"), ordered = TRUE),
         abs.diff = abs.diff*100) %>% #for visuals
  ggplot(aes(pheno, abs.diff)) +
  geom_violin(aes(x=pheno, y=abs.diff, fill=dataset, color=dataset), scale="count") +
  theme_linedraw(base_size = 11) +
  scale_fill_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  #WMV
geom_signif(y_position = c(29, 30.5, 4), xmin = c(0.7, 0.7, 1), 
              xmax = c(1, 1.3, 1.3), annotation = c("***","***", "***"),
              tip_length = 0, vjust = 0.6) +
  #GMV
  geom_signif(y_position = c(30, 31.5, 3), xmin = c(1.7, 1.7, 2), 
              xmax = c(2, 2.3, 2.3), annotation = c("***","***", "***"),
              tip_length = 0, vjust = 0.6) +
  #sGMV
  geom_signif(y_position = c(28, 29.5, 2.8), xmin = c(2.7, 2.7, 3), 
              xmax = c(3, 3.3, 3.3), annotation = c("***","***", "***"),
              tip_length = 0, vjust = 0.6) +
  #Ventricles
  geom_signif(y_position = c(24, 25.5, 7.5), xmin = c(3.7, 3.7, 4), 
              xmax = c(4, 4.3, 4.3), annotation = c("***","***", "***"),
              tip_length = 0, vjust = 0.6) +
  labs(y="Absolulte Centile Error", x = "Feature") +
  theme(plot.title = element_text(size=12))
global_cent_errs_plot
# ggsave("figs/global_centile_errors.jpeg", global_cent_errs_plot)
```

@@

# p_diff_annotate <- annotate_figure(p_diff)
# p_diff_annotate
```
plot w ref sites
```{r, eval=FALSE}
#get means w/in feature 
mean.cent.diffs.long <- diffs.df %>%
  dplyr::select(sex, dataset, pheno, pheno_abs.diff.list) %>%
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss", "cf.lm_refA", "cf.gam_refA", "cf.gamlss_refA"), ordered = TRUE)) %>%
  group_by(dataset) %>%
  summarize(across(starts_with("abs.diff_"), mean)) %>%
  ungroup() %>%
  pivot_longer(cols=starts_with("abs.diff_"), values_to="cent_abs.diff", names_to = "pheno", names_prefix = "abs.diff_") %>%
  # mutate(pheno=gsub(".z", "", pheno)) %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)),
      label = sub("_[^_]*_", "_", pheno))

mean.cent.diffs.long %>%
  dplyr::filter(dataset != "ukb_CN") %>%
  ggplot() +
  geom_histogram(aes(x=cent_abs.diff, fill=dataset, y = stat(width*density)), color="black", alpha=0.6, position="identity") +
  theme_linedraw(base_size = 11) +
  facet_grid(dataset~pheno_cat) +
  scale_y_continuous(labels = scales::percent) + 
  labs(y="Percent Features", x = "Mean Absolute Centile Error") +
  ggtitle("Absolute errors in centiles of brain structure features across ComBat processing pipelines")
```

@@

```{r, eval=FALSE}
subj_sum.df %>%
  dplyr::filter(dataset == "cf.gamlss" | dataset == "cf.gam" | dataset == "cf.lm") %>%
  mutate(mean_cent_abs.diff = mean_cent_abs.diff*100) %>% #for visuals
  ggplot() +
  geom_boxplot(aes(x=sex, y=mean_cent_abs.diff, fill=sex)) +
  labs(y= "Magnitude Centile Error", x = "ComBat Configurations") +
  facet_wrap(~dataset) +
  theme(legend.position="none") +
  ggtitle("Within-subject mean magnitude of error in centile scores across ComBat configurations")

@@

```{r,eval=FALSE}
#view combat gam and combat LS ns
ns.sex_diff_filt.gam <- sex_t_tests_in_feat.df %>%
  dplyr::filter(sig_fdr==FALSE & dataset =="cf.gam") %>%
  arrange(pheno)
ns.sex_diff_filt.gamlss <- sex_t_tests_in_feat.df %>%
  dplyr::filter(sig_fdr==FALSE & dataset =="cf.gamlss") %>%
  arrange(pheno)
```

@@

big_violin_plt <- plt.df %>%
  ggplot(aes(x=pheno, y=diff)) +
  geom_violin(aes(x=interaction(pheno,pheno_cat, sep = "&"), y=diff, fill=sex, color=sex)) +
  # geom_violin(aes(fill=sex, color=sex)) +
  theme_linedraw(base_size = 11) +
  labs(y="Centile Error", x = "Brain Feature") +
  theme(plot.title = element_text(size=12), axis.ticks.x = element_blank(), axis.text.x = element_blank(), panel.spacing.x = unit(.1, "lines"), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  stat_pvalue_manual(stat.test2, label = "p.adj.signif", label.size = 3, tip.length = 0, hide.ns = TRUE, remove.bracket = TRUE) +
  # facet_grid2(dataset ~ pheno_cat, labeller=labeller(dataset=dataset_names), scales="free_x", space = "free_x", switch="x", strip = custom_strip) +
  facet_wrap(~dataset, labeller=labeller(dataset=dataset_names), nrow=2) +
  guides(x = ggh4x::guide_axis_nested(delim = "&")) +
  theme(plot.title = element_text(size=12), axis.ticks.x = element_blank(), axis.text.x = element_blank(), ggh4x.axis.nesttext.x = element_text(angle = 90, vjust=0.4), legend.position="top") +
  labs(fill = "Sex", color="Sex")
  # ggtitle("Male and female centile errors")
big_violin_plt
ggsave("figs/big_sex_violin_plt.jpeg", big_violin_plt, width=12, height=6, units="in")
```

```{r, eval=FALSE}
big_violin_plt_wlabels <- plt.df %>%
  ggplot(aes(x=pheno, y=diff)) +
  geom_violin(aes(x=interaction(pheno,pheno_cat, sep = "&"), y=diff, fill=sex, color=sex)) +
  # geom_violin(aes(fill=sex, color=sex)) +
  theme_linedraw(base_size = 11) +
  labs(y="Centile Error", x = "Brain Feature") +
  theme(plot.title = element_text(size=12)) +
  stat_pvalue_manual(stat.test2, label = "p.adj.signif", label.size = 2.5, tip.length = 0, remove.bracket = TRUE) +
  # facet_grid2(dataset ~ pheno_cat, labeller=labeller(dataset=dataset_names), scales="free_x", space = "free_x", switch="x", strip = custom_strip) +
  facet_wrap(~dataset, labeller=labeller(dataset=dataset_names), nrow=2) +
  guides(x = ggh4x::guide_axis_nested(delim = "&")) +
  theme(plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust=0.4, size=6), ggh4x.axis.nesttext.x = element_text(angle = 90, vjust=0.4), legend.position="top") +
  labs(fill = "Sex", color="Sex")
  # ggtitle("Male and female centile errors")
big_violin_plt_wlabels
ggsave("figs/big_sex_violin_plt_wlabels.jpeg", big_violin_plt_wlabels, width=16, height=9, units="in")
```

@@

sex.var.plot <- ggplot(sex.var.plot.df) +
  theme_linedraw(base_size=12) +
  ggseg::geom_brain(atlas = dk_nomed, 
             position = position_brain(hemi ~ side),
             aes(fill = median_sex_diff)) +
  #scale_fill_gradient2() +
  # ggseg::geom_brain(data=med_wall, atlas = dk, 
  #            position = position_brain(hemi ~ side),
  #            aes(fill=median_sex_diff)) +
  facet_grid(dataset ~ pheno_cat, labeller = labeller(dataset = as_labeller(dataset_names))) + 
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA), aspect.ratio=2/3, plot.margin = margin(1,1,1,1, 'pt')) +
  paletteer::scale_fill_paletteer_c("grDevices::Cork", name = "Male - Female Median \nCentile Error", limits = c(-6, 6)) #
sex.var.plot
```

@@

sex.var.plot.global <- ggplot(sex.var.plot.global.df) +
  geom_rect(data = tp, fill="gray", xmin = -Inf,xmax = Inf,
            ymin = -Inf, ymax = Inf, alpha = 0.4) +
  ggseg::geom_brain(atlas = aseg_cerebrum, 
             aes(fill = median_sex_diff),
             side = c("coronal")) +
  #scale_fill_gradient2() +
  facet_grid(dataset~pheno_cat) + 
  theme_linedraw(base_size=12) +
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA), aspect.ratio=, plot.margin = margin(1,1,1,1, 'pt'), strip.text.y = element_blank()) +
  paletteer::scale_fill_paletteer_c("grDevices::Cork",  limits = c(-6, 6), name = "Male - Female Median \nCentile Error") #,
# sex.var.plot.global
```

@@

centile error diffs
```{r, message=FALSE}
centile.t.tests(no_ext, feature_list=pheno_abs.diff.list)
```

@@

plot w ref sites
```{r, eval=FALSE}
#get means w/in feature 
mean.z.diffs.long <- diffs.df %>%
  dplyr::select(sex, dataset, pheno, z.pheno_abs.diff.list) %>%
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss", "cf.lm_refA", "cf.gam_refA", "cf.gamlss_refA"), ordered = TRUE)) %>%
  group_by(dataset) %>%
  summarize(across(starts_with("abs.diff_"), mean)) %>%
  ungroup() %>%
  pivot_longer(cols=starts_with("abs.diff_"), values_to="z_abs.diff", names_to = "pheno", names_prefix = "abs.diff_") %>%
  mutate(pheno=gsub(".z", "", pheno)) %>%
  mutate(pheno_cat = as.factor(case_when(
      pheno %in% vol_list_global ~ "Global Volume",
      pheno %in% vol_list_regions ~ "Regional Volume",
      pheno %in% sa_list ~ "Regional SA",
      pheno %in% ct_list ~ "Regional CT",
      TRUE ~ NA_character_)),
      label = sub("_[^_]*_", "_", pheno))

mean.z.diffs.long %>%
  dplyr::filter(dataset != "ukb_CN") %>%
  ggplot() +
  geom_histogram(aes(x=z_abs.diff, fill=dataset, y = stat(width*density)), color="black", alpha=0.6, position="identity") +
  theme_linedraw(base_size = 11) +
  facet_grid(dataset~pheno_cat) +
  scale_y_continuous(labels = scales::percent) + 
  labs(y="Percent Features", x = "Mean Absolute Z-Score Error") +
  ggtitle("Absolute errors in zscores of brain structure features across ComBat processing pipelines")
```

@@

```{r, eval=FALSE}
subj_sum.df %>%
  dplyr::filter(dataset == "cf.gamlss" | dataset == "cf.gam" | dataset == "cf.lm") %>%
  ggplot() +
  geom_boxplot(aes(x=sex, y=mean_z_abs.diff, fill=sex)) +
  labs(y= "Magnitude Z Error", x = "ComBat Configurations") +
  facet_wrap(~dataset, scales="free_y") +
  theme(legend.position="none") +
  ggtitle("Within-subject mean magnitude of error in z-scores across ComBat configurations")

@@

```{r, message=FALSE}
z.sex_t_tests_in_feat.df <- sex.bias.feat.t.tests(diffs.df, feature_list=z.pheno_diff_list)

@@

<!-- ### W/o extremes -->
Are extreme z-scores (<-2 and >2) driving observed results?

@@

z.no.ext_merge %>%
  ggplot() +
  geom_boxplot(aes(x=type, y=z_abs.diff, fill=dataset)) +
  ggtitle("W/in feature average magnitude of z error, w/ and w/o extreme subjects")
```

@@

wmv_centile_fan <- ggplot(wmv.df) +
  geom_jitter(data = ukb_cn_df, aes(x=ukb_cn_df$age_years, y=ukb_cn_df$WMV), alpha=0.4, width=.2, color="lightgray") +
  #scale_colour_manual(values=c("#5AAE61FF", "#9970ABFF")) +
  geom_line(aes(x=age_years, y=centile_1, color=dataset, linetype=dataset)) +
  geom_line(aes(x=age_years, y=centile_2, color=dataset, linetype=dataset)) +
  #geom_line(aes(x=age_years, y=centile_3, color=dataset, linetype=dataset)) +
  # geom_line(aes(x=age_years, y=centile_4, color=dataset, linetype=dataset)) +
  geom_line(aes(x=age_years, y=centile_5, color=dataset, linetype=dataset), linewidth=1.5) +
  # geom_line(aes(x=age_years, y=centile_6, color=dataset, linetype=dataset)) +
  # geom_line(aes(x=age_years, y=centile_7, color=dataset, linetype=dataset)) +
  geom_line(aes(x=age_years, y=centile_8, color=dataset, linetype=dataset)) +
  geom_line(aes(x=age_years, y=centile_9, color=dataset, linetype=dataset)) +
  facet_wrap(~sex) + 
  scale_linetype_manual(values = c('ukb-CN-simsites'= "dotted", cf.gam = "solid", cf.gamlss = "solid", cf.lm = "solid"), name = "ComBat \nConfiguration", labels=dataset_names) +
  scale_color_manual(values = c('ukb-CN-simsites'= "black", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) + 
  geom_label(data=tmp_labels, aes(x=age_years, y=value, label=as.character(centile)), nudge_x = 0.35, size=2.5) +
  xlab("Age (yrs)") + ylab("White Matter Volume (mm3)") +
  theme_linedraw(base_size = 11) +
  theme(plot.title = element_text(size=12), legend.position="bottom")
wmv_centile_fan
```
Look at other phenotypes

@@

## FIGURE 1: METHODS

toy brain chart for figs, diagram portion done in canva

@@

not sure whether to include
```{r, eval=FALSE}
#look at sex distributions of ppts across sites
data.p <- subj_sum.df %>%
  count(sim.site, sex) %>% 
  group_by(sim.site) %>%
  mutate(prop = n / sum(n)) %>%
  ggplot(aes(x = sim.site, y = prop, fill = sex)) +
  geom_col() +
  theme_linedraw(base_size = 11) +
  ggtitle("Distributions of male and female subjects across simulated sites")
```

@@

```{r}
fig_2 <- ggarrange(
  wmv_centile_fan,
  ggarrange(global_cent_errs_plot, p_diff, ncol=1, nrow=2, heights = c(1.2, 2), common.legend = FALSE, labels=c(NA, "C"), vjust = c(-0.25)),
  ncol=2, nrow=1, 
  labels=c("A", "B"),
  widths=c(1.1, 1)
  #hjust=0.01,
  # align = "hv"
  )

fig_2_annotate <- annotate_figure(fig_2, top = text_grob("Figure 2. Choice of ComBat configuration can induce errors in brain feature centile scores",
               color = "black", hjust = 0, x = 0))
fig_2_annotate
ggsave("figs/figure_2.jpeg", fig_2_annotate, width=11, height=7, units="in")
```

## FIGURE 3

@@

fig_3 <- ggarrange(
  ggarrange(blank, 
            annotate_figure(
              ggarrange(sex.var.plot.global, sex.var.plot,
  ncol=2, nrow=1, 
  widths = c(1, 3.25),
  hjust=0.01,
  align = "hv",
  common.legend = TRUE, legend = "right"
  )),
  blank,
  ncol=3, nrow=1,
  widths=c(.5, 1, .5)),
  big_violin_plt,
  ncol=1, nrow=2, 
  #labels=c("A", "B"),
  #hjust=0.01,
  # align = "hv",
  heights=c(1, 1.8),
  common.legend = FALSE,
  labels=c("A", "B")
  )
# fig_2

fig_3_annotate <- annotate_figure(fig_3, top = text_grob("Figure 3. Sex-biases in centile score errors across ComBat configurations", color = "black", hjust = 0, x = 0))
fig_3_annotate
ggsave("figs/figure_3.jpeg", fig_3_annotate, width=11.5, height=10, units="in")
```
